\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}

\title{Minutes and Activity Sheets}
\date{}

\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\begin{document}
\maketitle
\tableofcontents
\newpage
\section{Introduction}

During this project, minutes were taken at every group meeting. The group would often meet immediately after a seminar, and also would meet
on Thursday when necessary. Activity sheets were also filled out by each member of the team, describing the work each member did during that week. 

\newpage
\section{Minutes}

\subsection{Meeting 1}

\textbf{Meeting Type}: Initial meeting.

\textbf{Meeting Date}: 18/02/16

\textbf{Meeting Start Time}: 15:09

\textbf{Meeting End Time}: 15:52

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Kea.

\textbf{Absence}: Jeremiah.

\textbf{Progress}: First meeting, everyone had quickly read the project brief.

\textbf{Actions}: All --- read project description, write notes, split it into major tasks. PERT-chart done by 28/02/2016. Read about Git and GitHub.

\textbf{Next Meeting}: 23/02/2016 14:00

\textbf{Additional Comments}: Decided to test, comment and document the project as we go. Talked about timetable, 3 weeks to get all requirements done, 6 weeks for coding and testing. Possible risks: trains being late, people not showing up, incompatible environments or OS – this can be solved by using Java, losing files or corrupt data – solved with GitHub, requirement changes. Decided our management is democratic decentralised. Going to use Slack and Github.

\subsection{Meeting 2}

\textbf{Meeting Type}: After-seminar progress meeting.

\textbf{Meeting Date}: 23/02/16

\textbf{Meeting Start Time}: 14:00

\textbf{Meeting End Time}: 14:15

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Kea, Jeremiah.

\textbf{Absence}: -

\textbf{Progress}: Checking progress on each PERT chart developed by each team member.

\textbf{Actions}: All --- Continue PERT chart development, read briefing. Jeremiah --- phase plan. Sal --- organisation plan. Dan --- conflict resolution plan, peer assessment plan. Kea, Regan --- functional requirements. Sam --- non-functional requirements, domain requirements.

\textbf{Next Meeting}: 01/03/2016 14:00

\textbf{Additional Comments}: -

\subsection{Meeting 3}

\textbf{Meeting Type}: After-seminar progress meeting.

\textbf{Meeting Date}: 01/03/16

\textbf{Meeting Start Time}: 14:00

\textbf{Meeting End Time}: 14:20

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Kea, Jeremiah.

\textbf{Absence}: -

\textbf{Progress}: Ensured all team members are on-track with their tasks as assigned on 23/02. Group discussion resolving clarifications/queries with tasks. Discussed potential high-level models of the system.

\textbf{Actions}: All --- continue working on assigned tasks.

\textbf{Next Meeting}: 08/03/2016 14:00

\textbf{Additional Comments}: -

\subsection{Meeting 4}

\textbf{Meeting Type}: After-seminar progress meeting.

\textbf{Meeting Date}: 08/03/16

\textbf{Meeting Start Time}: 14:00

\textbf{Meeting End Time}: 14:10

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Kea, Jeremiah.

\textbf{Absence}: -

\textbf{Progress}: All successfully completed assigned tasks (as per 23/02 meeting). On-track.

\textbf{Actions}: All --- experiment with potential high-level models for the system to share with the group at the next meeting on Thursday.

\textbf{Next Meeting}: 10/03/2016 15:00

\textbf{Additional Comments}: -

\subsection{Meeting 5}

\textbf{Meeting Type}: Review meeting to merge work on high-level project model.

\textbf{Meeting Date}: 10/03/16

\textbf{Meeting Start Time}: 15:00

\textbf{Meeting End Time}: 15:50

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Kea, Jeremiah.

\textbf{Absence}: -

\textbf{Progress}: Had each created a basic high-level model for the system.

\textbf{Actions}: All --- create lower-level model (add potential attributes, operations, add aggregation, abstraction etc.) from our starting point high-level model to merge at/after the seminar next week.

\textbf{Next Meeting}: 15/03/2016 13:00

\textbf{Additional Comments}: Need to clarify at some point - what kind of game statistics do we take? Order for turns --- decided to flip which team goes first each turn [EDIT - clarified later, ants move according to their identifiers which are allocated at the start of the match].

\subsection{Meeting 6}

\textbf{Meeting Type}: Design plan and PERT chart development meeting.

\textbf{Meeting Date}: 15/03/16

\textbf{Meeting Start Time}: 14:05

\textbf{Meeting End Time}: 14:30

\textbf{Attendance}: Regan, Sam, Dan, Arsalan, Jeremiah.

\textbf{Absence}: Kea (unwell).

\textbf{Progress}: All discussed actions and attributes of the model classes created so far. Assigned Regan as developer of 'core program'. Created plan for Git usage - probably use one 'master' branch for everything and a separate one for when the GUI is developed.

\textbf{Actions}: All --- Design models - lower level - look up and implement one each, based on current high-level design on GitHub.

\textbf{Next Meeting}: TBC.

\textbf{Additional Comments}: -

\subsection{Meeting 7}

\textbf{Meeting Type}: Review meeting with Kingsley.

\textbf{Meeting Date}: 05/04/16

\textbf{Meeting Start Time}: 13:00

\textbf{Meeting End Time}: 13:55

\textbf{Attendance}: Kea, Sam, Dan, Arsalan, Jeremiah.

\textbf{Absence}: Regan.

\textbf{Progress}: Discussed progress so far, in particular the sequence diagrams of the planning phase.

\textbf{Actions}: Jeremiah --- UML - World. Sal --- Revise sequence diagrams. Dan --- UML - Cell. Kea --- UML - Brain. Regan --- UML - Core. Sam --- UML - GUI, fix PERT chart.

\textbf{Next Meeting}: 12/04/2016 13:00

\textbf{Additional Comments}: -

\subsection{Meeting 8}

\textbf{Meeting Type}: Seminar meeting.

\textbf{Meeting Date}: 12/04/16

\textbf{Meeting Start Time}: 13:00

\textbf{Meeting End Time}: 13:55

\textbf{Attendance}: Regan, Sam, Dan, Jeremiah.

\textbf{Absence}: Arsalan, Kea.

\textbf{Progress}: Progress in finalising class diagrams. Updated PERT chart. Sal finished sequence diagrams.

\textbf{Actions}: All --- from last week, class diagramming tasks were assigned. These have a hard completion deadline of Thursday - after which point development will start. Sam and Jeremiah --- do draft of test specification (again by Thursday).

\textbf{Next Meeting}: 14/04/2016 15:00

\textbf{Additional Comments}: -

\subsection{Meeting 9}

\textbf{Meeting Type}: Very important meeting - arrange organisation of group for the next phase, discuss milestones, ensure on track for all deliverables.

\textbf{Meeting Date}: 15/04/16

\textbf{Meeting Start Time}: 15:00

\textbf{Meeting End Time}: 16:30

\textbf{Attendance}: Regan, Sam, Dan, Jeremiah, Arsalan, Kea.

\textbf{Absence}: -

\textbf{Progress}: Not discussed at this meeting.

\textbf{Actions}: Kea --- requirements: Convert functional requirements document from natural language to structured/form-based, programming: develop user interface. Dan --- user documentation: create instructional guide for users - how to write an ant-brain, ant-world, how to use the program, peer assessment plan: create plan for how points will be allocated amongst group members. Regan --- programming: implement ant core (game, tournament, brain, etc.). Sal and Jeremiah --- quality assurance: begin implementing tests for test-driven development where possible, write tests as developers implement classes. Jeremiah --- create an ant brain. Sam --- minor changes: revise high-level design - add associations, remove Grid class, update PERT chart - add ant brain design, additions to test specification - Gradle, JaCoCo, documentation, continuous integration, breakpoints, programming: implement parsers and world/cell/sense-related content.

\textbf{Next Meeting}: 19/04/2016 13:00

\textbf{Additional Comments}: -

\section{Activity Sheets}

\subsection{Week 03}

Arsalan Sadeghpour: Signed up to Github and Slack and setup a communication channel on Facebook.

Dan Read: Also signed into both Github and Slack. Through social media, established contact with team members.

Jeremiah Oluwakanmi:

Kea Tossavainen: Signed up to Github and Slack.

Regan Ware: Signed into GitHub and Slack

Sam Marsh: Set up Slack communication channel and GitHub repository. Added templates for quality manual documents.

\subsection{Week 04}

Arsalan Sadeghpour: Identified work breakdown structure of project and attempted a basic PERT Chart.

Dan Read: Went through the project. Together with team, began to divide tasks for each to do. Also devised a PERT chart.

Jeremiah Oluwakanmi

Kea Tossavainen: Wrote functional requirements with Regan.

Regan Ware: Worked with Kea on the functional requirements.

Sam Marsh: Read and took notes on project details, quality manual. Figured out main project tasks. Had a go at creating a PERT chart.

\subsection{Week 05}

Arsalan Sadeghpour: Did the Organisation Plan section of the Project Plan.

Dan Read: Completed the risk management task, with the conflict resolution embedded within.

Jeremiah Oluwakanmi:

Kea Tossavainen: Continued and completed functional requirements with Regan.

Regan Ware: Continued and completed the functional requirements with Kea.

Sam Marsh: Did the non-functional and domain requirements.

\subsection{Week 06}

Arsalan Sadeghpour: Attempted an initial high level model of the system to discuss with the group.

Dan Read: Designed a high-level overview of the project.

Jeremiah Oluwakanmi:

Kea Tossavainen: Sketched some high-level models, worked on all the documentation for submission next week.

Regan Ware: Sketched a high level model. Discussed the working of core and world interfunctionality

Sam Marsh: Designed high-level model of system. Added code coverage and continuous integration tools to main repository.

\subsection{Week 07}

Arsalan Sadeghpour: Setup version control within my IDE.

Dan Read:

Jeremiah Oluwakanmi:

Kea Tossavainen: Worked on documentation.

Regan Ware: Connected NetBeans to Git for version control. Assigned to the `core program'.

Sam Marsh: Created revised PERT chart.

\subsection{Break 01}

Arsalan Sadeghpour: I have created a folder structure detailing the high level designs, and low level designs. I worked on the high level design by creating a Use Case Diagram representing an Ant's behaviour and 2 Activity Diagrams representing the game execution behaviour and the gameplay and scoring functionality.

Dan Read: Began to delve deeper into the design, by looking at the various methods that different objects in the code will need, building towards a class-diagram.

Jeremiah Oluwakanmi:

Kea Tossavainen: Combined all the documents and submitted through Study Direct.

Regan Ware: Prepared for core design. How each component fits together to ease transition into coding. Tested first commit to Github (unsuccessfully, committed and never pushed)

Sam Marsh: 

\subsection{Break 02}

Arsalan Sadeghpour: I completed the detailed design by creating sequence diagrams for each Use Case and I created a State Diagram representing Ant Brain Behaviour.

Dan Read: Continued with the methods for the class diagram.

Jeremiah Oluwakanmi:

Kea Tossavainen: Planned some diagrams.

Regan Ware: Read through sequence diagrams to aid in core class creation. Minor changes to core UML diagram.

Sam Marsh: Began coding the visual interface.

\subsection{Week 08}

Arsalan Sadeghpour: Started working on the Acceptance Criteria document by looking at the Requirements document.

Dan Read: Create an in-depth look at the cell section of the class diagram.

Jeremiah Oluwakanmi:

Kea Tossavainen: Worked on diagrams. Started planning GUI.

Regan Ware: Began core UML diagram.

Sam Marsh: Did diagrams for GUI. Fixed PERT chart.

\subsection{Week 09}

Arsalan Sadeghpour: Upon review of the UML designs in Week 8, I have edited all the sequence diagrams showing the adapted structure and pushed the designs to Github.

Dan Read: With group, reviewed the UML designs.

Jeremiah Oluwakanmi:

Kea Tossavainen: Reviewed UML diagrams with the group.

Regan Ware: Finalised core UML diagrams.

Sam Marsh: Small modifications to high-level design. Updated PERT chart. Complete test specification.

\subsection{Week 10}

Arsalan Sadeghpour: Created Scope and Test Plan sections of the Test Specification document.

Dan Read: Received instructions on various documentation to do, in order to meet deadline.

Jeremiah Oluwakanmi:

Kea Tossavainen: Worked on GUI diagrams.

Regan Ware: Added Game, Match, Tournament and Player classes and added base functionality

Sam Marsh: Implement brain parser, world parser, world, cell, sense-related content. Create acceptance criteria. Update UML diagram.

\subsection{Week 11}

Arsalan Sadeghpour: Developed Unit Tests and Documented the Test Procedures section of the Test Spec. Created Release Tests for the Software. Documented Test Results using automatically generated HTML document.

Dan Read: Undertook both the user documentation and the short report describing success and any failures.

Jeremiah Oluwakanmi:

Kea Tossavainen: Finished GUI UML diagram, did structured functional requirements.

Regan Ware: Work on integrating the core program to run matches. Looping through ants running murder or step, rounds, tournament logic and statistics

Sam Marsh: Programming and documentation - world (including contest world generator), cells, ant behaviour.

\end{document}